Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-09-21 manuscript/manuscript.tex
Start editing the conclusion
Not much to change. This part is really good. Just removed some
unnecessary details.

We have developed a new methodology that computes the gravitational fields
generated by a tesseroid with continuously variable density in depth.
It numerically solves the integrals that define the gravitational potential,
its gradient and the Marussi tensor components through the Gauss-Legendre
Quadrature (GLQ), which essentially consists in approximating the
gravitational fields of the tesseroids with the effect of point masses located
on nodes of the Quadrature.

Instead of enhancing the accuracy of the method by increasing the order of the
GLQ on each integration, we make use of the pre-existing modified adaptive
discretization algorithm and a new density-based discretization algorithm.

The former one divides the tesseroid by half if the ratio of the distance to
the computation point and its size is lower than a predefined distance-size
ratio $D$.
This algorithm is introduced in order to minimise the error when the
computation point is close to the tesseroid, in which case the effect of the
point masses becomes more noticeable and the approximation lose precision.
Following this idea, we can summarise that the distance-size ratio $D$
controls the accuracy of the method: a higher value of $D$ generates more
divisions of the tesseroids, thus more point masses, what leads to a more
precise approximation.
Nevertheless, this algorithm is not sufficient to guarantee the accuracy of
the method in case of tesseroid with variable density.

For this reason we have developed a density-based discretization algorithm that
divides the tesseroid on the radius at which the \emph{maximum variation} of
the density function takes place, only if a certain inequation that relates
this \emph{maximum variation} with a predefined delta ratio $\delta$ holds.
The number of subdivisions is indirectly controlled by this delta
ratio $\delta$, and thus the accuracy of the computation.
This new algorithm is intended to minimise the error due to the inability of
the GLQ to produce precise approximations in case of highly varying density:
the information about the density function is summed up with the values that
it assumes at the node of the quadrature.
Increasing the subdivisions of the tesseroid where the \emph{maximum
variation} of the density takes place becomes an efficient way to reduce this
kind of error.

>>>>

We have developed a new methodology to compute the gravitational fields
generated by a tesseroid with a density given by a continuous function of depth.
It numerically solves the integrals that define the gravitational potential,
its gradient, and the Marussi tensor components through the Gauss-Legendre
Quadrature (GLQ).
The accuracy of the numerical integration is automatically controlled by an adaptive
discretization algorithm and a new density-based discretization algorithm.
The former divides the tesseroid in half if the ratio of the distance to the computation
point and the size of the tesseroid is lower than a predefined distance-size ratio $D$.
This algorithm minimises the integration error when the computation point is close to
the tesseroid.
Nevertheless, the adaptive discretization alone is not sufficient to guarantee the
accuracy of the method in case of tesseroids with variable density.

To overcome this challenge, we have developed a density-based discretization algorithm
that divides the tesseroid on the points at which the maximum variations of the density
function takes place.
The density-based discretization is performed before adaptive discretization as a type
of pre-processing step.
The number of divisions performed, and thus the accuracy of the computation, is
controlled by the delta ratio $\delta$.
This new algorithm is intended to minimise the error due to the inability of
the GLQ to produce precise approximations of highly variable density functions.
